### 2016-03-22 reply_to_reviewers.md

> Page 2, paragraph 3, lines 39-41: This sentence is a bit awkward—perhaps
> remove the comma?

Done

> Page 3, paragraph 1, line 58: Other recently developed R packages that relate
> to rotl might be mentioned, including taxize (taxonomy congruence),
> phyloGenerator (generate phylogenies for ecologists) and pez (for calculating
> suites of metrics for community phylogenetics).

We added a paragraph about the use of phylogenetics in community ecology,
inclding a description of R packages that can be used for these analysis [Pg
Line]

@@

> Page 4, point #2: So not all studies that can be queried through the API were
> included in the OTL? Perhaps this can be explained a bit more here (or in the
> “Getting trees from studies” subsection).

We added the number of studies that have been submitted through the curator
app, and the number of studies that contribute to the synthetic tree to clarify
this point.

"As of March 2016, the Open Tree of Life project stores 7755 trees from 3399 
studies (each having between 0 and 61 trees), and 477 of these trees are used 
to assemble the synthetic tree."

@@

> Page 9, line 150: What type of metadata can be extracted from a study? Is it
> just the citation (which is the example given in “How to use rotl?” vignette)?

There is a lot more information associated with each study. We re-worded the
paragraph to mention some of them.

"Metadata about the study (e.g., citation information, information about
the curator for the study, and other technical information regarding the import
of this study) can be obtained using the function `get_study_meta`

### 2016-03-22 manuscript.Rnw
update tag version used to generate the manuscript

The recognition of the importance of phylogenies to account for the statistical
non-independence of species in comparative methods, and the recent development
of methods to explore trait evolution or changes in diversification rates, have
driven the need for accurate phylogenies. However, there is often a discrepancy
between taxa targeted by comparative methods, and taxa for which phylogenies are
available. We believe that by providing an easy-to-use interface to obtain
phylogenies for an arbitrary set of taxa directly in R, \texttt{rotl} will be
useful in a wide variety of contexts.

@@

\texttt{rotl} is free, open source, and released under a Simplified BSD
license. Stable versions are available from the CRAN repository
(\url{https://cran.r-project.org/package=rotl}), and development versions are
available from GitHub (\url{https://github.com/ropensci/rotl}). This manuscript
was built using version 0.4.1.999-rotl-ms.1
(\url{https://github.com/ropensci/rotl/tree/v0.4.1.999-rotl-ms.1}). The package
is under active development, and authors welcome bug reports or feature requests
via the GitHub repository.  The source for this manuscript is available on
GitHub (\url{https://github.com/fmichonneau/rotl-ms}).

>>>>

The recognition of the importance of phylogenies to account for the statistical
non-independence of species in comparative methods, the recent development of
methods to explore trait evolution or changes in diversification rates, and
attempts to incorporate the evolutionary history of species forming ecological
communities, have driven the need for accurate phylogenies. However, there is
often a discrepancy between taxa targeted by studies wanting to use phylogenetic
information, and taxa for which phylogenies are available. Typically, the latter
result from focused studies of taxonomic groups, while the former encompass
species found in a given geographical location or ecosystem. We believe that by
providing an easy-to-use interface to obtain phylogenies for an arbitrary set of
taxa directly in R, \texttt{rotl} will be useful in a wide variety of contexts.

@@

\texttt{rotl} is free, open source, and released under a Simplified BSD
license. Stable versions are available from the CRAN repository
(\url{https://cran.r-project.org/package=rotl}), and development versions are
available from GitHub (\url{https://github.com/ropensci/rotl}). This manuscript
was built using version 0.5.0.901-rotl-ms.2
(\url{https://github.com/ropensci/rotl/tree/v0.5.0.901-rotl-ms.2}). The package
is under active development, and authors welcome bug reports or feature requests
via the GitHub repository.  The source for this manuscript is available on
GitHub (\url{https://github.com/fmichonneau/rotl-ms}).
